---
title: "complex_syllabus"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{complex-syllabus}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
Now, we will walk through a moderately complex syllabus and its Gradebook implementation with 5 students in the class. Start with what this syllabus would look like on a class website.

## Syllabus

## Policy File 
Here is what the policy file looks like:
```yaml
`r xfun::file_string(system.file("extdata", "complex_syllabus.yaml", package = "gradebook"))`

```

```{r, include = FALSE}
library(gradebook)
yaml::read_yaml(system.file("extdata", "complex_syllabus.yaml", package = "gradebook"))
# to be replaced with gradebook::read_policy()
```

## Gradescope Assigments File
Here is what the gradescope assignments file looks like:

<div style="height: 300px; overflow: auto;">
```{r, echo=FALSE}
knitr::kable(complex_syllabus_data)
```
</div>

## Workflow


### Grade Calculations
First, read in your YAML policy file.

```{r}
policy <- yaml::read_yaml(system.file("extdata", "complex_syllabus.yaml", package = "gradebook"))
```
`validate_policy()` checks the formatting of the policy file.
```{r}
policy <- validate_policy(policy, gs = complex_syllabus_data)
```
Finally, `get_grades()` grades your assignments based on your policy file.
```{r}
grades <- get_grades(policy = policy, gs = complex_syllabus_data)
```
The output of the grades looks like:
<div style="height: 300px; overflow: auto;">
```{r, echo=FALSE}
knitr::kable(grades)
```
</div>