---
title: "Case Study: Complex Syllabus"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{complex-syllabus}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Now, we will walk through a complex syllabus and its Gradebook implementation with 5 students in the class. Start with what this syllabus would look like on a class website.

## Syllabus

The final student's grade is computed from *1) labs, 2) midterm exam and 3) final exam*. Their grade will be computed as follows:

-   Labs 20%
    - Lab 1, Lab 2, and Lab 3
    - They are aggregated equally
    - Each "Lab \#" is compiled of two parts, which are weighted by their respective point value: "Lab #.1" & "Lab #.2"
      - For example: if Lab 1.1 is worth 15 points and Lab 1.2 is worth 5 points, then Lab 1.1 accounts for 75% of Lab 1 score. 
    - The lowest 1 assignment is dropped
    - All components of the lab individually experience a lateness penalty:
      - 10% reduction of the score, if assignment is submitted late but within 24 hours of the deadline
      - 30% reduction of the score, if assignment is submitted after 24 hours of the deadline deadline
-   Midterm 40%
-   Final Exam 40%


## Policy File

Here is what the policy file looks like:

``` yaml
`r xfun::file_string(system.file("extdata", "complex_syllabus.yaml", package = "gradebook"))`
```

```{r, include = FALSE}
library(gradebook)
yaml::read_yaml(system.file("extdata", "complex_syllabus.yaml", package = "gradebook"))
```

## Gradescope Assigments File

Here is what the gradescope assignments file looks like:

::: {style="height: 300px; overflow: auto;"}
```{r, echo=FALSE}
complex_syllabus_data <- readr::read_csv(system.file("extdata", "complex_syllabus_data.csv", package = "gradebook"))
knitr::kable(complex_syllabus_data)
```
:::

## Workflow


**Overall grade** is calculated using the three categories, with the weights as shown above; This is represented by `Overall Grade` with an aggregation of `weighted_mean`.

The **Midterm** and **Final Exam** categories contain only a single assignment, as shown in the `complex_syllabus_data` file, which is usually downloaded from gradescope.

The **Labs** category is compiled of **3 nested categories**: *"Lab 1"*, *"Lab 2"*, *"Lab 3"*,  and each has 2 corresponding assignments: *"Lab 1.1"*, *"Lab 1.2"*, *"Lab 2.1"*, *"Lab 2.2"*, *"Lab 3.1"*, *"Lab 3.2"*.

### Grade Calculations


```{r, message = FALSE}
complex_syllabus_data <- readr::read_csv(system.file("extdata", "complex_syllabus_data.csv", package = "gradebook"))

policy <- yaml::read_yaml(system.file("extdata", "complex_syllabus.yaml", package = "gradebook"))

validated_policy <- validate_policy(policy, gs = complex_syllabus_data)

grades <- get_grades(policy = validated_policy, gs = complex_syllabus_data)
```
First, read in your YAML policy file. `validate_policy()` checks the formatting of the policy file. Finally, `get_grades()` grades your assignments based on your policy file.

The output of the grades looks like:

::: {style="height: 300px; overflow: auto;"}
```{r, echo=FALSE}
knitr::kable(grades)
```
:::

Disclaimers:

-   The `weights` of a category with aggregation `weighted_mean` should be corresponding order with the `assignments.`

-   Categories cannot have the same name as any other assignment name.
