---
title: "Format of a Policy File"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Format of a Policy File}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Most college courses have a section of the syllabus that defines the rules for calculating final course grades from individual assignment grades. In this package, that information is stored in a *policy file*.

Here is an example of a what a policy file might look, stored as a .yml file.

```{r, results="asis", echo = FALSE}
library(gradebook)
library(yaml)

cat(paste("```yaml\n", as.yaml(policy_demo), "\n```"), sep = "\n")
```

### Contents of a policy file

As you can see [Here is where we describe how the policy file is structured.].

For details on the exact specifications of the policy file, please see [link to place in code that validates the schema].

### `policy_demo` in `gradebook`

`gradebook` stores a sample policy file, `policy_demo`, that can be used to explore the functionality of the package. The policy file is the one shown at the top of this vignette as a yaml file and is stored in the package as an R list.

```{r}
library(gradebook)
policy_demo
```

