---
title: "Case Study: A Moderate Syllabus"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{moderate-syllabus}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
Now, we will walk through a moderately complex syllabus and its Gradebook implementation with 5 students in the class. Start with what this syllabus would look like on a class website.

## Syllabus


The final student's grade is computed from *1) homework assignments, 2) midterm exam, and 3) the final exam*. Their grade will be computed as follows:

-   Homework 20%
    - Homework 1, Homework 2, Homework 3, Homework 4, Homework 5
    - All assignments are aggregated equally
    - The lowest 2 assignments are dropped
-   Midterm 40%
-   Final Exam 40%


## Policy File 
Here is what the policy file looks like:
```yaml
`r xfun::file_string(system.file("extdata", "moderate_syllabus.yaml", package = "gradebook"))`

```

```{r, include = FALSE}
library(gradebook)
yaml::read_yaml(system.file("extdata", "moderate_syllabus.yaml", package = "gradebook"))
```

## Gradescope Assigments File
Here is what the gradescope assignments file looks like:

<div style="height: 300px; overflow: auto;">
```{r, echo=FALSE}
knitr::kable(moderate_syllabus_data)
```
</div>

## Workflow

**Overall grade** is calculated using the three categories, with the weights as shown above; This is represented by `Overall Grade` with an aggregation of `weighted_mean`.

The **Midterm** and **Final Exam** categories contain only a single assignment, as shown in the `moderate_syllabus_data` file, which is usually downloaded from gradescope.

The **Homework** category is compiled of five assignments: *"Homework 1"*, *"Homework 2"*, *"Homework 3"*, *"Homework 4"*, *"Homework 5"* in the `moderate_syllabus_data`.

### Grade Calculations
First, read in your YAML policy file.

```{r}
policy <- yaml::read_yaml(system.file("extdata", "moderate_syllabus.yaml", package = "gradebook"))
```
`validate_policy()` checks the formatting of the policy file.
```{r}
policy <- validate_policy(policy, gs = moderate_syllabus_data)
```
Finally, `get_grades()` grades your assignments based on your policy file.
```{r}
grades <- get_grades(policy = policy, gs = moderate_syllabus_data)
```

The output of the grades looks like:

::: {style="height: 300px; overflow: auto;"}
```{r, echo=FALSE}
knitr::kable(grades)
```
:::

Disclaimers:

-   The `weights` of a category with aggregation `weighted_mean` should be corresponding order with the `assignments.`

-   Categories cannot have the same name as any other assignment name.
