---
title: "Case Study: Moderate Syllabus"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{moderate-syllabus}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
Now, we will walk through a moderately complex syllabus and its Gradebook implementation with 5 students in the class. Start with what this syllabus would look like on a class website.

## Syllabus


The final student's grade is computed from *1) homework assignments, 2) midterm exam, and 3) the final exam*. Their grade will be computed as follows:

-   Homework 20%
    - Homework 1, Homework 2, Homework 3, Homework 4, Homework 5
    - All assignments are aggregated equally
    - The lowest 2 assignments are dropped
    - All components of the lab individually experience a lateness penalty:
      - 10% reduction of the score, if assignment is submitted late but within 24 hours of the deadline
      - 30% reduction of the score, if assignment is submitted after 24 hours of the deadline
-   Midterm 40%
-   Final Exam 40%


## Policy File 
Here is what the policy file looks like:
```yaml
`r xfun::file_string(system.file("extdata", "moderate_syllabus.yaml", package = "gradebook"))`

```

```{r, include = FALSE}
library(gradebook)
yaml::read_yaml(system.file("extdata", "moderate_syllabus.yaml", package = "gradebook"))
```

## Gradescope Assigments File
Here is what the gradescope assignments file looks like:

<div style="height: 300px; overflow: auto;">
```{r, echo=FALSE}
moderate_syllabus_data <- readr::read_csv(system.file("extdata", "moderate_syllabus_data.csv", package = "gradebook"))
knitr::kable(moderate_syllabus_data)
```
</div>

## Workflow

**Overall grade** is calculated using the three categories, with the weights as shown above; This is represented by `Overall Grade` with an aggregation of `weighted_mean`.

The **Midterm** and **Final Exam** categories contain only a single assignment, as shown in the `moderate_syllabus_data` file, which is usually downloaded from gradescope.

The **Homework** category is compiled of five assignments: *"Homework 1"*, *"Homework 2"*, *"Homework 3"*, *"Homework 4"*, *"Homework 5"* in the `moderate_syllabus_data`.

### Grade Calculations

```{r, message = FALSE}
moderate_syllabus_data <- read_gs(system.file("extdata", "moderate_syllabus_data.csv", package = "gradebook"))

policy <- read_policy(system.file("extdata", "moderate_syllabus.yaml", package = "gradebook"))

grades <- get_grades(policy = policy, gs = moderate_syllabus_data)
```
First, read in your YAML policy file. `validate_policy()` checks the formatting of the policy file. Finally, `get_grades()` grades your assignments based on your policy file.

The output of the grades looks like:

::: {style="height: 300px; overflow: auto;"}
```{r, echo=FALSE}
knitr::kable(grades)
```
:::

## Syllabus as a Grading Script
Here is the coded version of the same syllabus.
```{r}
# function to implement lateness policy
lateness_penalty <- function(score_vec, lateness_vec){
  lateness <- lubridate::period_to_seconds(lubridate::hms(lateness_vec))/60
  dplyr::case_when(
    lateness == 0 ~ score_vec,
    lateness <= 1440 ~ 0.9*score_vec,
    .default = 0.7*score_vec
  )
}

#function to drop lowest two grades
two_drops <- function(data){
  apply(dplyr::select(data, `Homework 1`, `Homework 2`, `Homework 3`, `Homework 4`,`Homework 5`), 1, function(x) sort(x, decreasing = TRUE)[1:3]) |> t()
}

data_with_lateness <- moderate_syllabus_data |>
  # calculate percentages
  dplyr::mutate(
    `Homework 1` = `Homework 1`/`Homework 1 - Max Points`,
    `Homework 2` = `Homework 2`/`Homework 2 - Max Points`,
    `Homework 3` = `Homework 3`/`Homework 3 - Max Points`,
    `Homework 4` = `Homework 4`/`Homework 4 - Max Points`,
    `Homework 5` = `Homework 5`/`Homework 5 - Max Points`,
    `Midterm Exam` = `Midterm Exam`/`Midterm Exam - Max Points`,
    `Final Exam` = `Final Exam`/`Final Exam - Max Points`
  ) |>
  #lateness
  dplyr::mutate(
    `Homework 1` = lateness_penalty(`Homework 1`,`Homework 1 - Lateness (H:M:S)`),
    `Homework 2` = lateness_penalty(`Homework 2`,`Homework 2 - Lateness (H:M:S)`),
    `Homework 3` = lateness_penalty(`Homework 3`,`Homework 3 - Lateness (H:M:S)`),
    `Homework 4` = lateness_penalty(`Homework 4`,`Homework 4 - Lateness (H:M:S)`),
    `Homework 5` = lateness_penalty(`Homework 5`,`Homework 5 - Lateness (H:M:S)`)
  ) 
script_grades <- data_with_lateness |>
  # calculate category grade for "Homework" 
  dplyr::mutate( 
    `Homework` = rowMeans(two_drops(data_with_lateness))) |>
  # calculate final Overall Grade
  dplyr::mutate(`Overall Grade` = 0.4*`Homework` + 0.2*`Midterm Exam` + 0.4*`Final Exam`) 
```

And, as you can see, the computations align.
```{r}
library(ggplot2)
tibble::tibble(
  `Script Grades` = script_grades$`Overall Grade`,
  `Gradebook Grades` = grades$`Overall Grade`
) |>
  ggplot(aes(x = `Gradebook Grades`, y = `Script Grades`)) + 
  geom_point(size = 2) + geom_abline(slope = 1, color = "red")
```
```{r, echo = FALSE}
if (!all(script_grades$`Overall Grade` == grades$`Overall Grade`))
  stop("Script grades and Gradebook grades do not align for moderate syllabus vignette.")
```


### Disclaimers:

-   The `weights` of a category with aggregation `weighted_mean` should be corresponding order with the `assignments.`

-   Categories cannot have the same name as any other assignment name.
