---
title: "Writing Policy Files"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{policy-files}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

There are two ingredients that are needed to calculate course grades with `gradebook`: a data frame containing assignment scores and a file that encodes the grading policies often described in a syllabus. We call that file a *policy file*.

Policy files are stored as [.yaml](https://www.cloudbees.com/blog/yaml-tutorial-everything-you-need-get-started) files, a simple format for storing hierarchical data in a text file with minimal markup. Here is an example of a policy file for a course with a fairly simple grading scheme.

```yaml
`r xfun::file_string('extdata/simple_policy.yaml')`
```

Once you have written your policy file, you can read it into R as a list.

```{r}
yaml::read_yaml("inst/extdata/simple_policy.yaml")
# to be replaced with gradebook::read_policy()
```

