---
title: "Building a Policy File"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{policy-files}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

There are two ingredients that are needed to calculate course grades with `gradebook`: a data frame containing assignment scores and a file that encodes the grading policies often described in a syllabus. We call that file a *policy file*.

Policy files are stored as [.yaml](https://www.cloudbees.com/blog/yaml-tutorial-everything-you-need-get-started) files, a simple format for storing hierarchical data in a text file with minimal markup. Here is an example of a policy file for a course with a fairly simple grading scheme.

Note that category names cannot be the same as any assignment names.

```yaml
`r xfun::file_string(system.file("extdata", "policy_demo.yaml", package = "gradebook"))`

```

Once you have written your policy file, you can read it into R as a list.

```{r}
yaml::read_yaml(system.file("extdata", "policy_demo.yaml", package = "gradebook"))
# to be replaced with gradebook::read_policy()
```

## Recognized Keys

There are a series of recognized keys with corresponding values. Each key represents a certain type of calculation in your syllabus, and the value determines the specifics of this calculation.

### Category

Every single category must have the `category` key. This is the name of the subcategory and must be unique from all other category names and all assignment names as well.

### Assignments

The `assignments` key determines which assignments or subcategories are used to determine the category score. The values for this key must match assignments in the Gradescope data or subcategories determined in the same policy file. This can be left blank, but this means that this category score will not be factored into any of the grade calculations and will be ignored.

### Score

The `score` key determines how the percentage of an assignment score is calculated. At the moment, there is only one valid value for this key:

-   `raw_over_max`: the percentage of an assignment score is the point-value of the assignment divided by the maximum points of the assignment.

    -   Note: if `score` is not explicitly determined, this is the *default*.

### Aggregation

The `aggregation` key determines how the various assignment scores are aggregated together in order to calculate the category score. These are the corresponding values for this key:

-   `equally_weighted`: the category score is the average of the assignment scores with no regard to the relative point-values of the assignments.

    -   Note: if `aggregation` is not explicitly determined, this is the *default*.

-   `weighted_by_points`: the category score is the weighted average of the assignment scores with the weights determined by the relative point-values of the assignments.

-   `max_score`: the category score is the maximum of the assignment scores.

-   `min_score`: the category score is the minimum of the assignment scores.

-   `weighted_mean`: the category score is the weighted average of the assignment scores with the weights being explicitly determined using the `weight` key in the nested categories.

    -   Note: this is often reserved for the final overall-grade calculation.

-   `none`: this is reserved for when a category is comprised of only one assignment; hence no aggregation is necessary because the category score is simply the assignment score.

### Lateness

The `lateness` key is used to write lateness policies. The values for this key are divided into threshold functions and penalty functions.

Threshold functions determine the valid lateness period for which the penalty is applied. Here are the possible threshold functions:

-   `until`: this marks the lateness-period up until and including the specified value.

-   `after`: this marks the lateness-period after and including the specified value.

-   `between`: this marks the lateness-period between and including the two specified values.

Here are the possible penalty functions:

-   `add`: add the specified value to the assignment score if the assignment's lateness falls within its respective threshold.

    -   Note: this is often used to give bonuses for turning an assignment in on-time.

-   `scale`: scale the assignment score by the specified factor if the assignment's lateness falls within its respective threshold.

    -   Note: this is often used to reduce an assignment score if the assignment is turned in late.

-   `set_to`: set the assignment score to the specified value if the assignment's lateness falls within its respective threshold.

    -   Note: this is often used to set an assignment score to zero if the assignment is turned in too late.

See `Case Study: Moderate Syllabus` to view an example of a lateness policy

### Drop N Lowest

The `drop_n_lowest` key is used to drop *n* of the lowest assignments scores. This *n*-value can take any integer that is less than the total number of assignments in the category.

## Nesting and Inheritance

## Importance of Order
