---
title: "Case Study: A Simple Syllabus"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{simple-syllabus}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(yaml)
```

Now, we will walk through a simple syllabus and its Gradebook implementation. Start with what this syllabus would look like on a class website.

## Syllabus

The entirety of a student's grade is determined by their grades on two midterms and the final exam. Their grade will be computed as follows:

-   Homework 20%
-   Midterm 40%
-   Final Exam 40%

## Policy File 
Here is what the policy file looks like:
```yaml
`r xfun::file_string(system.file("extdata", "simple_syllabus.yaml", package = "gradebook"))`

```

```{r}
yaml::read_yaml(system.file("extdata", "simple_syllabus.yaml", package = "gradebook"))
# to be replaced with gradebook::read_policy()
```


## Workflow

This grade is calculated using three categories, with the weights as shown above; this is represented by `Overall Grade` with an aggregation of `weighted_mean`. The Midterm and Final Exam categories contain only a single assignment, as shown in the `simple_gs` file. The Homework category is compiled of two assignments: "Homework 1" and "Homework 2" in the `simple_gs`.